Pre working group data exploration: Julianna

### 2024-07-03 julianna_data_exploration.Rmd
Getting rid of my rogue R proj which I think(?) was a mistake
Checking pull status
Smol amount of code

# load packages
require(here)
require(tidyverse)
```

@@

```{r}

```

>>>>

# load packages
require(here) # relative file paths
require(tidyverse) # data wrangling
require(vegan) # community/diversity analyses
```

@@

These are the most recent file versions done by Lauren as of July 2, 2024

```{r}
allbenthos <- read_csv(here("data", "allbenthicdata_cleaned_colnames.csv")) 
algae <- read_csv(here("data", "algaeonly_cleaned_colnames.csv"))
```

# Calculate algal diversity metrics

Make a spp matrix to use with vegan

```{r}
# matrix of just species and their relative percent covers
algae %>% 
  select(-year, -location, -site, -habitat, -site_habitat, -transect, -quadrat) -> sppMat

# metadata info that is in the same order (can re-join after)
algae %>% 
  select(year, location, site, habitat, site_habitat, transect, quadrat) -> sppMeta
```

```{r}
diversity(algae)
```

# Join algae and coral data

```{r}
allbenthos %>% 
  select(year, location, site, habitat, site_habitat, transect, quadrat, coral) %>% 
  full_join(algae) -> coralAlg
```
